%-----------------------------------------------------------------------------
% Beginning of biblio.tex
%-----------------------------------------------------------------------------

\bibliographystyle{amsalpha}
\begin{thebibliography}{A}

\bibitem [1]{}  Murphy, K. P. (2012). Machine learning: a probabilistic perspective. MIT press.

\bibitem [2]{} Bishop, C. M. (2006). Pattern Recognition. Machine Learning.

\bibitem [3]{} Hastie, T., R. Tibshirani, and J. Fried-
man (2001). The Elements of Statis-
tical Learning. Springer.

\bibitem [4]{Sch2002} Schoelkopf, B. and A. Smola (2002). Learning with Kernels: Support Vector Machines, Regularization, Optimization, and Beyond. MIT Press.

\bibitem [5]{Koller} Koller, D. and N. Friedman (2009). Probabilistic
Graphical Models: Principles and Techniques. MIT Press.

\bibitem [6]{Aro1950} Aronszajn, N. (1950). Theory of reproducing kernels. Transactions of the American mathematical society, 68(3), 337-404.
\bibitem [7] {Sch1998} Schoelkopf, B., A. Smola, and K.-R.Mueller (1998).
Nonlinear component analysis as a kernel eigenvalue problem. Neural
Computation 10, 1299 – 1319.

\bibitem [8]{Jaakk1998} Jaakkola, T. and D. Haussler (1998). Exploiting generative models in discriminative classifiers. In NIPS, pp.487–493

\bibitem [9] {Kri2005} Krishnapuram, B., L. Carin, M. Figueiredo, and A. Hartemink (2005). Learning sparse bayesian classifiers: multi-class formulation, fast algorithms, and generalization bounds. IEEE Transaction on Pattern Analysis and Machine Intelligence.

\bibitem [10] {Tip2001} Tipping, M. (2001). Sparse bayesian learning and the relevance vector machine. J. of Machine Learning Research 1, 211–244.

\bibitem [11]{Has2009} Hastie, T., R. Tibshirani, and J. Friedman (2009). The Elements of Statistical Learning. Springer. 2nd edition

\bibitem [12]{Hof2008} Hofmann, T., Scholkopf, B., Smola, A. J. (2008). Kernel methods in machine learning. The annals of statistics, 1171-1220

\bibitem [13]{Suy2002} Suykens, J. A., Van Gestel, T., De Brabanter, J. (2002). “Least squares support vector machines”. World Scientific.

\bibitem [14] {Cor1995} Cortes, C., Vapnik, V. (1995). Support-vector networks. Machine learning, 20(3), 273-297.

\bibitem [15] {Ste2008} Steinwart, I.,Christmann, A. (2008). Support vector machines. Springer Science and Business Media.

\bibitem [16]{GR1992} Gelman, A., and D. B. Rubin. 1992. Inference from Iterative Simulation Using Multiple Sequences. Statistical Science 7: 457–511.

\bibitem [17]{BG1997} Brooks, S. P., and A. Gelman. 1997. General Methods for Monitoring Convergence of Iterative Simulations. Journal of Computational and Graphical Statistics 7: 434–455.

\bibitem [18]{HMC} Duane, S., A. Kennedy, B. Pendleton, and D. Roweth (1987). Hybrid Monte Carlo. Physics Letters B 195(2), 216–222

\bibitem [19]{Jebara2004} Jebara, T., R. Kondor, and A. Howard (2004). Probability product kernels. J. of Machine Learning Research 5, 819–844

\bibitem [20]{BleiVI} David M. Blei, Alp Kucukelbir and Jon D. McAuliffe (2017) Variational Inference: A Review for Statisticians, Journal of the American Statistical Association, 112:518, 859-877

\end{thebibliography}

%\end{{thebibliography}
%-----------------------------------------------------------------------------
% End of biblio.tex
%-----------------------------------------------------------------------------
